Reducing Acceptance Condition\\ of Emerson-Lei Automata

### 2021-10-13 paper/main.tex
abstract added!

\begin{abstract}
  We present an QBF-based algorithm that reduces the number of
  acceptance sets of transition-based Emerson-Lei automata.
\end{abstract}

>>>>

\begin{abstract}
  The formalism called \emph{transition-based Emerson-Lei automata
    (TELA)} generalizes many traditional kinds of automata over
  infinite words including Büchi, co-Büchi, Rabin, Streett, and parity
  automata. Transitions in TELA are marked with acceptance marks and
  accepting formulas are boolean combinations of terms saying that a
  particular mark has to be visited infinitely or finitely often in an
  accepting run. Algorithms processing these automata can be very
  sensitive to the number of different acceptance marks. We introduce
  two techniques reducing the number of acceptance marks in a TELA
  without altering its structure and the represented language. One
  technique represents a standard approach based on relations among
  acceptance marks in individual strongly connected components of the
  automaton. The other technique constructs quantified boolean formula
  (QBF) queries that ask a QBF solver for an acceptance condition with
  fewer acceptance marks and the placement of these marks in the
  automaton structure. Both techniques are implemented and experiments
  show that the number of acceptance marks in TELA produced by
  state-of-the-art tools ltl3tela, Rabinizer~4, and SPOT can be
  sometimes reduced. In the case of Rabinizer~4, we reduced the
  cummulative number of acceptance marks to less than one half.
\end{abstract}
